---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# understress

<!-- badges: start -->
[![R-CMD-check](https://github.com/Reckziegel/understress/workflows/R-CMD-check/badge.svg)](https://github.com/Reckziegel/understress/actions)
[![R-CMD-check](https://github.com/Reckziegel/understress/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Reckziegel/understress/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> Know more about marginal PDFs estimation error

The goal of `understress` is to decompose the estimation error that arises from 
marginal distributions under different correlation environments.

By using `understress` the econometrician can better understand where the sources 
of error come from and the size of their impact on current models.

## Installation

You can install the development version of `understress` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/understress")
```

## Example

```{r example}
library(understress)
stress_test_multivariate_normal_distribution(.simulations = 2000)
```

